---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The code below downloads and reads the data. It also does some very basic processing to ensure the dates are set as date date types. We also load the dplyr library, which will be used later.

```{r loaddata}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
library(dplyr)
fileURL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
localFileName <- "activity.zip"
download.file(fileURL, localFileName)
unzip(zipfile = localFileName)
activityData <- read.csv("activity.csv", nrows=3000)

activityData$date <- as.Date(activityData$date)
```


## What is mean total number of steps taken per day?

```{r totalmeanstepsperday}
dailySummary <- activityData %>%
    group_by(date) %>%
    summarise(dailyTotalSteps=sum(steps))


# FIX clean up labels
hist(dailySummary$dailyTotalSteps, breaks = 10)

meanStepsPerDay <- mean(dailySummary$dailyTotalSteps, na.rm = TRUE)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
